### 2022-12-16 Draft_GFC.tex
Version avant les vacances avec linkage des parties

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%
\usepackage{amsmath,amssymb,amsthm,amsfonts,amstext,amsbsy,amscd,stmaryrd}
\usepackage{amssymb,amsmath,comment,subcaption,graphicx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{cancel}
\usepackage{tikz}
\usepackage{subcaption} 
\usetikzlibrary{patterns}
\usepackage{xcolor}
\usepackage{bbm}
\usepackage{float}
\usepackage{color}
\usepackage{relsize}
\newcommand{\modif}[1]{{\begin{modification}#1\end{modification}}}
\newcommand{\ele}[1]{{\color{red}#1}}
%\UseRawInputEncoding
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{mathrsfs}
\newcommand{\rmd}{{\mathrm{d}}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Z}{\mathbb{Z}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\operatorname{\mathbb{E}}}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\Cov}{\mathrm {Cov}}
\newcommand{\rme}{{\rm e}}
\renewcommand{\tilde}{\widetilde}
\renewcommand{\hat}{\widehat}
\newcommand{\TC}{\mathrm{TC}}
\newcommand{\TaC}{\mathrm{TaC}}
\newcommand{\LTC}{\mathrm{LTC}}
\newcommand{\LP}{\mathrm{LP}}
\newcommand{\Per}{\mathrm{Per}}
\theoremstyle{Theorem}
\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Definition}[Theorem]{Definition}
\newtheorem{remark}{Remark}
\renewcommand{\labelitemi}{\textperiodcentered}
\allowdisplaybreaks
\usepackage{ifpdf}
\ifpdf
\else
\usepackage{graphicx}
\DeclareGraphicsExtensions{.eps,.jpg,.png}
\fi
\usepackage{epstopdf}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

@@

\begin{Definition}[Perimeter of a binary image $Z^{\scriptscriptstyle (m)}$]\label{defPerimetre}~\\
For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) =~\sum_{\scriptscriptstyle x: w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle (i)}_{m}} f_{t}^{\scriptscriptstyle (i)}(x)$ the  sum of all vertical contributions for $i = 1$ and horizontal ones for $i = 2$. Then, the perimeter of the binary image $Z$ is given by

@@

\mathcal{P}_{m}(t) := \mathcal{P}_{m}^{\scriptscriptstyle (1)}(t) + \mathcal{P}_{m}^{\scriptscriptstyle (2)}(t).

@@

@@

\section{Statistics of the perimeter} 

@@

Let us start this study by investigating the first moment of the perimeter.
\begin{Proposition}[First moment of the perimeter] 

@@

We assume that $\left(X_x \right)_{x \in \mathbb{G}_{m}}$ is a stationary Gaussian centered with unit variance random field. Let us denote \linebreak by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in~[-1, 1]$. The expected value of the perimeter in \eqref{eq:6} is  given \linebreak by $$\mathbb{E}\left(\mathcal{P}_{m}(t)\right) = m(m-1)\sum_{1}^{2}\mathbb{E}\left(f^{(i)}(t) \right)$$ where

@@

& = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right|\right\}}\right).
\mathbb{E}\left(f^{(i)}(t)\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\right) \\
& = \mathbb{E}\left(\mathbbm{1}_{\left\{ - \sqrt{2(1-\rho(e_i))}\left|U\right| \leq 2t - \sqrt{2(1+\rho(e_i)}V \leq \sqrt{2(1-\rho(e_i))}\left|U\right| \right\}}\right) \\

@@

with $(U, V) \sim \mathcal{N}(0,I_{2})$, thus 

@@

In order to have convergence when $m$ goes to infinity, one has to normalize the perimeter with the area of the window ($m^2$), considering $\frac{1}{m^2}\mathcal{P}_{m}(t)$.

@@

The total variation of an image $u \in L^{1}_{loc}(\Omega)$ is given by $\int_{\Omega}|\nabla u|dx$ which is equal by the coarea formula to $\int_{\mathbb{R}}\mathcal{P}(t)dt$ with $\mathcal{P}(t)$ being the perimeter associated to the level set of the image $u$ at level $t$ .

@@

@@

Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result concerning the expected perimeter at level $t$:

@@

Where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance $\tilde{\rho}$. 

@@

Let $t \in \mathbb{R}$ we can prove this result by considering  the function $$h:x\mapsto \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right) - \Phi\left(\dfrac{2t - \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right).
$$

@@

h'(x) &= \frac{2\exp(-t^2/(1+x))}{2\sqrt{2\pi}(1-x)^{1/2}(1+x)^{3/2}}\\
& \int_{0}^{\infty}\exp\left(-\frac{N^{2}}{(1+x)}\right)\left(-4N\cosh\left(\frac{t\sqrt{2(1-x)}}{1+x}\right) + 2t\sqrt{2(1-x)}\sinh\left( \frac{t\sqrt{2(1-x)}}{1+x}\right)\right)dN \\
& = \frac{-2\exp(-t^2/(1+x))(1+x)}{\sqrt{2\pi}(1-x)^{1/2}(1+x)^{3/2}}\\
& = \frac{-2}{\sqrt{2\pi(1-x^2)}}\exp(-t^2/(1+x)),

@@

for all $|x| < 1, \; h'(x) < 0$, thus, $h$ is a strictly decreasing function. 

@@

\subsection{Covariance of the perimeter for two thresholds}

@@

\pagebreak

@@

Now that we know more about the second moment of the perimeter, we can construct a Multi-directional multivariate CLT that will lead us to an isotropy test, the following Central Limit Theorem is proved with a lesser condition on the covariance of the field.
In order to get the CLT we have to add some assumptions on the covariance structure of the field, we will need the following  assumptions 
\item \textbf{$(A_{1})$} $\lim_{n \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-y)$ exists.
\item \textbf{$(A_{2})$} $\lim_{n \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-~y)^{2}$ exists.

>>>>

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%
\usepackage{amsmath,amssymb,amsthm,amsfonts,amstext,amsbsy,amscd,stmaryrd}
\usepackage{amssymb,amsmath,comment,subcaption,graphicx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{cancel}
\usepackage{tikz}
\usepackage{subcaption} 
\usetikzlibrary{patterns}
\usepackage{xcolor}
\usepackage{bbm}
\usepackage{float}
\usepackage{color}
\usepackage{relsize}
\usepackage{diagbox}
\newcommand{\modif}[1]{{\begin{modification}#1\end{modification}}}
\newcommand{\ele}[1]{{\color{red}#1}}
%\UseRawInputEncoding
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{mathrsfs}
\newcommand{\rmd}{{\mathrm{d}}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Z}{\mathbb{Z}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\operatorname{\mathbb{E}}}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\Cov}{\mathrm {Cov}}
\newcommand{\rme}{{\rm e}}
\renewcommand{\tilde}{\widetilde}
\renewcommand{\hat}{\widehat}
\newcommand{\TC}{\mathrm{TC}}
\newcommand{\TaC}{\mathrm{TaC}}
\newcommand{\LTC}{\mathrm{LTC}}
\newcommand{\LP}{\mathrm{LP}}
\newcommand{\Per}{\mathrm{Per}}
\theoremstyle{Theorem}
\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Definition}[Theorem]{Definition}
\newtheorem{remark}{Remark}
\renewcommand{\labelitemi}{\textperiodcentered}
\allowdisplaybreaks
\usepackage{ifpdf}
\ifpdf
\else
\usepackage{graphicx}
\DeclareGraphicsExtensions{.eps,.jpg,.png}
\fi
\usepackage{epstopdf}
\usepackage{array}
\usepackage{enumitem}
\newcounter{Ax}
\newcommand{\itemA}{%
    \addtocounter{Ax}{1}
    \item[A\theAx.]}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

@@

\begin{Definition}[Directional perimeter of a binary image $Z^{\scriptscriptstyle (m)}$]\label{defPerimetre}~\\
For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t)$ the sum of all contributions over the $i$th direction (vertical and horizontal). Then, the directional perimeter of the binary image $Z^{\scriptscriptstyle (m)}$ is given by

@@

\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) =~\sum_{\scriptscriptstyle x: w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle (i)}_{m}} f_{t}^{\scriptscriptstyle (i)}(x).

@@

Then, the perimeter of $Z^{\scriptscriptstyle (m)}$ is given by $\mathcal{P}_{m}(t) := \mathcal{P}_{m}^{\scriptscriptstyle (1)}(t) + \mathcal{P}_{m}^{\scriptscriptstyle (2)}(t)$.

@@

\section{Statistics of the oriented perimeter} 

@@

Let us start this study by investigating the first moment of the oriented perimeter.
\begin{Proposition}[First moment of the directional perimeter] 

@@

We assume that $\left(X_x \right)_{x \in \mathbb{G}_{m}}$ is a stationary Gaussian centered with unit variance random field. Let $i \in \{1,2\}$ and let us denote by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in [-1, 1]$. The expected value of the perimeter in \eqref{eq:6} is  given by $$\mathbb{E}\left(\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t)\right) = m(m-1)\mathbb{E}\left(f^{(i)}(t) \right)$$ where

@@

& = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right|\right\}}\right). \\
& = \mathbb{E}\left(\mathbbm{1}_{\left\{ - \sqrt{2(1-\rho(e_i))}\left|U\right| \leq  \sqrt{2(1+\rho(e_i)}V -2t \leq \sqrt{2(1-\rho(e_i))}\left|U\right| \right\}}\right) \\

@@

@@

To have convergence when $m$ goes to infinity, one has to normalize the perimeter with the area of the window $S$, ($m^2$), thus considering $\frac{1}{m^2}\mathcal{P}_{m}(t)$.

@@

\textcolor{red}{
It is possible to link the total variation of an image $u \in L^{1}_{loc}(\Omega)$ which is given by $\int_{\Omega}|\nabla u|dx$ to its perimeter, by applying the coarea formula, $\int_{\Omega}|\nabla u|dx = \int_{\mathbb{R}}\mathcal{P}(t)dt$ with $\mathcal{P}(t)$ being the perimeter associated to the level set of the image $u$ at level $t$.}

@@

\textcolor{red}{Let us now study the monotonic properties of the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance~$\rho$.}

@@

\label{powertest}
\textcolor{red}{Let $\overline{X}, \tilde{X}$ be two stationary centered Gaussian random fields with unit variance, and $\bar{\rho}, \tilde{\rho}$ their respective covariance structure, we  have the following result regarding their associated expected oriented perimeter at level $t$:}

@@

@@

Let $t \in \mathbb{R}$ we can prove this result by considering  the function \begin{align*} 
h: (-1,1) &\longrightarrow \mathbb{R}, \\
x & \longmapsto \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right) - \Phi\left(\dfrac{2t - \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right),

@@

h'(x) & = \mathbb{E}\left( \left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)'\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)\right. \\
& \hspace{5cm} \left. - \left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)'\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right)\\
& = \mathbb{E}\left(\frac{-2|N| -t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right. \\
& \hspace{6cm}  \left. - \frac{2|N| - t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right) \\
& = \frac{1}{2(1+x)\sqrt{1-x^2}}\mathbb{E}\left(\left(-2|N| -t\sqrt{2(1-x)}\right)\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right. \\
& \hspace{5.5cm}  \left. - \left(2|N| - t\sqrt{2(1-x)}\right)\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right) \\
& = \frac{\exp(-t^2/(1+x))}{2\sqrt{2\pi}(1+x)\sqrt{1-x^2}}\\
&\hspace{0.5cm} \mathbb{E}\left(\left(-2|N| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|N|\sqrt{2(1-x)}}{1+x}\right)\exp\left(\frac{-N^{2}(1-x)}{2(1+x)}\right)\right. \\
&\hspace{2cm}\left. - \left(2|N| - t\sqrt{2(1-x)}\right)\exp\left(\frac{t|N|\sqrt{2(1-x)}}{1+x}\right)\exp\left(\frac{-N^{2}(1-x)}{2(1+x)}\right)\right) \\
& = \frac{\exp(-t^2/(1+x))}{4\pi(1+x)\sqrt{1-x^2}}\\
&\hspace{0.5cm} \int_{-\infty}^{\infty}\exp\left(-\frac{y^2}{1+x}\right)\left(\left(-2|y| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|y|\sqrt{2(1-x)}}{1+x}\right)\right. \\
&\hspace{5cm}\left. - \left(2|y| - t\sqrt{2(1-x)}\right)\exp\left(\frac{t|y|\sqrt{2(1-x)}}{1+x}\right)\right)dy \\ 
& = \frac{\exp(-t^2/(1+x))}{2\pi(1+x)\sqrt{1-x^2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
&\hspace{0.5cm} \int_{0}^{\infty}\left(\left(-2|y| -t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y+t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right. \\
&\hspace{5cm}\left. - \left(2|y| - t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y-t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right)dy \\
& = \frac{\exp(-t^2/(1+x))}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
& \hspace{2cm} \left(\int_{\frac{t}{2}\sqrt{2(1-x)}}^{\infty}-2z\exp\left(-\frac{z^2}{1+x}\right)dz + \int_{-\frac{t}{2}\sqrt{2(1-x)}}^{\infty}-2z\exp\left(-\frac{z^2}{1+x}\right)dz \right)\\
& = \frac{-2\exp(-t^2/(1+x))(1+x)}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\\
& = \frac{-\exp(-t^2/(1+x))}{\pi\sqrt{(1-x^2)}},

@@

for all $|x| < 1, \; h'(x) < 0$ thus, $h$ is a strictly decreasing function. 

@@

\textcolor{red}{Thus, the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ is strictly decreasing, in particular if $\rho(e_1) \neq \rho(e_2) $\linebreak then~$\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right) \neq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)$.\\ 
Now, if the field $X$ is isotropic, one consequence would be that $\rho(e_{1}) = \rho(e_{2})$ which implies~$\frac{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)} = 1$. Thus, having a Central Limit Theorem for the variable $\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t)$  would allow us to construct an isotropy test using the oriented perimeter of the field $X$.}
In order to establish the CLT, we need to add some assumptions on $\rho$ the covariance structure of the field $X$.
\begin{enumerate}
  \itemA 
 $\begin{aligned}[t]
 \label{conditionTCL1}
\lim_{m \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-y)\; \text{exists}.
\end{aligned}$
\itemA $\begin{aligned}[t]
 \lim_{m \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-~y)^{2}\; \text{exists}.
\end{aligned}$
\end{enumerate} 
\textcolor{red}{TCL}
\begin{proof} For the sake of simplicity, we will prove the CLT for $r=1$, the generalized case is made by following the same procedure. Using the Cramèr-Wold method, we need to prove that for each $(a_1, a_2) \in \mathbb{R}^{2}$, we have 
\frac{a_{1}}{m}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t)\right)\right) + \frac{a_{2}}{m}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t)\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}(t)\right) 
with $\sigma^{2}(t) = \lim_{m \to \infty} \mathbb{V}\left( \frac{a_{1}}{m}\mathcal{P}^{\scriptscriptstyle (1)}(t) + \frac{a_{2}}{m}\mathcal{P}^{\scriptscriptstyle (2)}(t) \right)$.
We first need to recall some notations that were introduced in the first section \eqref{fi}. We denote by $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2}$ and let~$a_{1}, a_{2}, t \in \mathbb{R}$, $x=(x_{1}, x_{2}) \in \mathbb{G}_{m}$ and $i \in \{1,2\}$.  We recall as introduced in \eqref{fi}
Let us denote the 4-dimensional Gaussian vector by $\mathbb{X}_{x_1, x_2} = (X_{x_1, x_2}, X_{x_1 + 1, x_2}, X_{x_2, x_1+1}, X_{x_2, x_1} )$ and $g_{t} : \mathbb{R}^{4} \to \mathbb{R}$, 
Note that $0 \leq f_{t}^{\scriptscriptstyle (i)}(0) \leq 1$ \textit{a.s.}, thus, \textit{a.s.},$\mathbb{E}\left(g_{t}\left(\mathbb{X}_{\scriptscriptstyle  0, 0}\right)^{2}\right) < (a_{1} + a_{2})^{2}$. In order to apply Theorem $2$ in \cite{arcones} and get the convergence, \\
\big[\textcolor{blue}{ $r^{(p,q )}(k) = \mathbb{E}\left(X^{p}_{m} X^{q}_{m+k}\right)$for $k\in Z$ and $1 < p, q < d$, where $m$ is any integer so large that $m, m + k > 1$. Suppose that \\
$\lim_{n \to \infty} n^{-1} \sum_{j,k = 1}^{n}r^{(p,q )}(j-k) < \infty$ and $\lim_{m \to \infty} n^{-1}\sum_{j,k = 1}^{n}(r^{(p,q )}(j-k))^{2} < \infty$}\big]\\
we should insure that 
\lim_{m \to \infty} m^{-2} \sum_{x \in \mathbb{G}_{m}}\sum_{y \in \mathbb{G}_{m}} \mathbb{E}\left(\mathbb{X}^{(p)}_{x}\mathbb{X}^{(q)}_{y}\right) < \infty \; \text{and} \; \lim_{m \to \infty} m^{-2} \sum_{x \in \mathbb{G}_{m}}\sum_{y \in \mathbb{G}_{m}} \left(\mathbb{E}\left(\mathbb{X}^{(p)}_{x}\mathbb{X}^{(q)}_{y}\right)\right)^{2} < \infty,
with $\mathbb{X}^{(p)}_{x}$ being the $p$-coordinate of the $4$-dimensional vector $\mathbb{X}_{x}$, then applying the stationarity hypothesis it amounts to the following
\lim_{m \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-y) < \infty \;  \text{and} \; \lim_{m \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-~y)^{2} < \infty.
Under $(A1)$ and $(A2)$, we can apply Theorem $2$ in \cite{arcones} we get that 
m^{-1} \sum_{(x_1, x_2) \in \mathbb{G}_{m}} g_{\scriptscriptstyle t}\left(\mathbb{X}_{x_1, x_2}\right) - \mathbb{E}\left(g_{\scriptscriptstyle t}\left(\mathbb{X}_{x_1, x_2}\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}(t)\right),
\sigma^{2}(t) := \mathbb{E}\left(\big[g_{t}(\mathbb{X}_{0}) - \mathbb{E}\left(g_{t}(\mathbb{X}_{0})\right)\big]^{2}\right) \\
& \hspace{-4cm}+ 2 \sum_{x_{1}, x_{2} = 1}^{\infty} \mathbb{E}\left(\big[g_{t}(\mathbb{X}_{0}) - \mathbb{E}\left(g_{t}(\mathbb{X}_{0})\right)\big]\big[g_{t}(\mathbb{X}_{x_1,x_2}) - \mathbb{E}\left(g_{t}(\mathbb{X}_{x_1, x_2})\right)\big]\right)
Re-writing the sum we get
\sum_{(x_1, x_2) \in \mathbb{G}_{m}} g_{t}\left(\mathbb{X}_{x_1, x_2}\right) - \mathbb{E}\left(g_{t}\left(\mathbb{X}_{x_1, x_2}\right)\right) & = \sum_{x_1 = 0}^{m-2}\sum_{x_2 = 0}^{m-1} g_{t}\left(\mathbb{X}_{x_1, x_2}\right) - \mathbb{E}\left(g_{t}\left(\mathbb{X}_{x_1, x_2}\right)\right) \\
&=  a_{1}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t)\right)\right) - a_{2}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t)\right)\right),
Thus
\frac{a_{1}}{m}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t)\right)\right) + \frac{a_{2}}{m}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t)\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}(t)\right) 
Let  $t \in \mathbb{R}$, and $\mathcal{P}^{\scriptscriptstyle  (i) }(t)$ be the oriented perimeter over direction $i$, introduced in Definition \ref{defPerimetre} computed at level $t$ let us denote by $\mu_{i}(t)) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)\right)$. Then, it holds that,
with $\tilde{\sigma}^{2}(t) = \frac{(\tilde{\sigma}_{\scriptscriptstyle 1,1}(t)\mu_{2}(t))^{2} - 2\mu_{2}(t)\mu_{1}(t)\tilde{\sigma}_{\scriptscriptstyle 1,2}(t)^{2} +(\tilde{\sigma}_{\scriptscriptstyle 2,2}(t)\mu_{1}(t))^{2}}{\mu_{2}(t)^4} \in (0, \infty)$. \\
Let $t \in \mathbb{R}$  and  $R_{m}(t) := \cfrac{\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t)}{\mathcal{P}^{\scriptscriptstyle  (2) }_{m}(t)}$. Then, under $H_{0}$, it holds that
and $\tilde{\sigma}^{2}(t) = \frac{2\left(\tilde{\sigma}_{\scriptscriptstyle 1,1}^{2}(t) \, - \, \tilde{\sigma}_{\scriptscriptstyle 1,2}^{2}(t)\right)}{\mu_{2}(t)^2}$.
Consider the consistent empirical estimator $\hat{\sigma}_{m,n}(t):= \frac{1}{m^2}\hat{\mathbb{V}\left(R_{m}(t)\right)}$ of $\tilde{\sigma}^{2}(t)$, where $\hat{\mathbb{V}\left(R_{m, n}(t)\right)}$ is the empirical variance of the considered ratio computed with Montecarlo $= n$. Then, from \ref{deltamethodgeneralprop}, it holds that 
$$ \frac{1}{m\sqrt{\hat{\sigma}_{m,n}(t)}}\left(R_{m}(t) - 1 \right) = \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m}(t)\right)}}}\left(R_{m}(t) - 1 \right)   \xrightarrow[m \to \infty]{d, H_{0}} \mathcal{N}\left(0, 1 \right).$$
Take a confidence level $\alpha \in (0,1)$ and set $q_{1-\frac{\alpha}{2}}$ such that $\mathbb{P}\left(|\mathcal{N}\left(0,1\right)| \leq  q_{1-\frac{\alpha}{2}} \right) = 1 - \frac{\alpha}{2}$. We define the symmetric accessible test $\hat{\phi}_{m, n}(t)$ with asymptotic level $\alpha$ as 
\hat{\phi}_{m,n}(t)= \mathbbm{1}_{\left\{ \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}\left|R_{m}((t) - 1 \right| \geq q_{1- \frac{\alpha}{2}} \right\}}
\begin{remark}(Power of the statistical test at a level $t$) In Remark \ref{powertest} we showed that the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ is strictly decreasing, thus, if $\rho(e_1) \neq \rho(e_2)$ thus $\frac{\mathbb{E}\left(\mathcal{P}^{1}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{2}(t)\right)} \neq 1$. 
Let $X$ be a stationary, isotropic centered Gaussian field with covariance function given by $\rho(x) = (1 -3||x||_{2}/3C + (||x||_{2}/2C)^{3})\mathbbm{1}_{||x||_{2} < C}, x \in \mathbb{R}^2$
Let ${Y(x; a, b, \theta): x \in \mathbb{R}^{2}}$ be a random field equal in distribution to  $\{X(Ax): x\in \mathbb{R}^{2}\}$, where 
A:= \begin{pmatrix} a & 0 \\ 0 & b\end{pmatrix} \begin{pmatrix} \cos(\theta) & \sin(\theta) \\ -\sin(\theta) & \cos(\theta)\end{pmatrix} 
with $a, b \in \mathbb{R}^{2}$ and $\theta \in [0, \pi)$, the field $Y$ is also Gaussian with covariance function given by  $\rho_{X}(x) = (1 - 3||Ax||_{2}/2C + (||Ax||_{2})^{3}/2C^{3})\mathbbm{1}_{||Ax||_{2} < C},$, note that $a\neq b$ if and only if $Y$ is anisotropic. We chose to illustrate the computations of the statistics of the perimeter, using this covariance structure, and the value $\theta = 0$ and $a = 1$. 
    {\includegraphics[scale=0.3]{EsperanceUnedirection.pdf}}
 \caption{In each panel, we represent the values of first moment of the oriented perimeter in direction $2$ computed for different values of $b$, the theoretical curve Equation \eqref{propFisrtmoment} is depicted using a blue color (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$, for different values of $b = 1, 2.5, 5, 10$ and $C = 40$. }

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.4]{TestaniRatiopvalue.pdf}}
    \hspace{0.2cm} 
 \caption{$p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.1, 1.2, 1.5, 2$ and $C = 40$.}
\label{fig2}
\end{figure}

\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
\hline
\diagbox{b}{t} & 0.2 &  0.3 &  0.4 &  0.5 &  0.6 &  0.7 &  0.8 &  0.9  \\ \hline
1  & 0.9866 &   0.9638 &  0.9971 &  0.9867 &  0.9674 &  0.9951 &  0.9754 &  0.9918  \\ \hline
1.1 & 0 &  0 &  0 &  0 &  0 &  0 &  0 &  0.0007  \\ \hline
1.2 & 0 &  0 &  0 &  0 &  0 &  0 &  0 &  0   \\ \hline 
1.5 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0   \\ \hline
2 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0  \\ \hline
\end{tabular}
\end{center}

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.4]{TestaniRatiopvaluetheta.pdf}}
    \hspace{0.2cm} 
 \caption{We represent $p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1.1$ and $\theta = \pi/3, \pi/4, \pi/5, \pi/6, \pi/8 $ and $C = 40$.}
\label{fig2}
\end{figure}
\subsection{Theroretical and numerical study of the covariance of the perimeter}

@@

@@
